Clinical prediction with localized modeling using similarity-based cohorts: A scoping review

### 2024-03-19 docs/Localized-Modeling/Localized-Modeling.Rmd
update analysis & finalize manuscript for resubmission

  \usepackage{soul}
  \definecolor{lightblue}{rgb}{.80,.90,1}
  \sethlcolor{lightblue}

@@

The `r nrow(tab_synthesis)` included studies were analyzed based on several characteristics, and we report and describe some observations here (Table \ref{tab:synthesis}). The studies were published in a variety of journals, with some of greater frequency, though no single journal published more than 3. The journal _Evolving Systems_ published 2 of the included studies, _Artificial Intelligence in Medicine_ published 3, _Hindawi - Journal of Healthcare Engineering_ published 3, and _PLOS One_ published 2.

@@

```{r framework, fig.align='center', out.width="100%", echo=FALSE}
#| fig.cap =
#| "General framework for localized models.
#|  Dashed arrows indicate optional steps."
knitr::include_graphics("Fig5.pdf")
```

@@

```{r methods, fig.align='center', out.width="100%", echo=FALSE}
#| fig.cap =
#| "Frequency of recurring methodological elements across included studies."
knitr::include_graphics("Fig4.png")
```

>>>>

  \usepackage{soul}
  %%\definecolor{hlcolor}{rgb}{.80,.90,1}
  \definecolor{hlcolor}{rgb}{1,1,1}
  \sethlcolor{hlcolor}

@@

The `r nrow(tab_synthesis)` included studies were analyzed based on several characteristics, and we report and describe some observations here (Table \ref{tab:synthesis}). The studies were published in a variety of journals, with some of greater frequency, though no single journal published more than 3. The journal _Evolving Systems_ published 2 of the included studies, _Artificial Intelligence in Medicine_ published 3, _Hindawi - Journal of Healthcare Engineering_ published 3\hl{, \emph{Evolving Systems} published 2}, and _PLOS One_ published 2.

@@

```{r framework, fig.align='center', out.width="100%", echo=FALSE}
#| fig.cap =
#| "General framework for localized models.
#|  Dashed arrows indicate optional steps."
knitr::include_graphics("Fig4.pdf")
```

@@

```{r methods, fig.align='center', out.width="100%", echo=FALSE}
#| fig.cap =
#| "Frequency of recurring methodological elements across included studies."
knitr::include_graphics("Fig5.png")
```
